\documentclass[12pt]{report}

% --------------------
% Packages
% --------------------
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{tocloft}
\usepackage{graphicx}
\usepackage{amsmath, amssymb}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{hyperref}

% --------------------
% Spacing
% --------------------
\onehalfspacing

% --------------------
% Chapter formatting
% --------------------
\titleformat{\chapter}
  {\normalfont\bfseries\Large}
  {\thechapter}
  {1em}
  {}

% --------------------
% Document
% --------------------
\begin{document}

% ====================Thesis Title
% Title Page
% ====================
\begin{titlepage}
\centering
\vspace*{1in}

{\Large \textbf{Using Computer Vision for PIV Analysis}}\\[1.5in]

{\large MIE498Y: Research Thesis}\\[0.5in]

\textbf{Han Hu}\\
1008797553\\[1in]

Supervisor: Prof. Pierre E. Sullivan\\[1in]

Date

\vfill
\end{titlepage}

% ====================
% Front Matter
% ====================
\pagenumbering{roman}

% --------------------
% Abstract (not listed in ToC)
% --------------------
\chapter*{Abstract}
The abstract is generally 100 to 200 words, single-spaced in block form, placed in the centre of a separate page.

\newpage

% --------------------
% Acknowledgements
% --------------------
\chapter*{Acknowledgements}
Acknowledgements (to persons and/or supporting agencies).

\newpage

% --------------------
% Table of Contents
% --------------------
\tableofcontents
\newpage

% --------------------
% List of Symbols
% --------------------
\chapter*{List of Symbols}

\begin{tabular}{ll}
Symbol & Definition \\
\hline
$A$ & Example symbol \\
$B$ & Example definition \\
\end{tabular}

\newpage

% --------------------
% List of Figures
% --------------------
\listoffigures
\newpage

% --------------------
% List of Tables
% --------------------
\listoftables
\newpage

% ====================
% Main Thesis
% ====================
\pagenumbering{arabic}

\chapter{Introduction}
Particle Imagery Velocimetry (PIV) is a flow visualization technique that measures the instantaneous 
velocity of the fluid flow by calculating the displacement of laser illuminated particles in two different 
images taken. Upon adequate post processing, planar velocity fields can be obtained from raw data of the 
experiment. The use of laser in the experiment resulted in measurement errors near object boundaries 
due to the reflection from the object. To resolve this issue, masks are created to exclude certain 
areas from the solve. Traditionally, manual masking is performed by researchers to define zones of 
exclusion. However, such method is impractical for measurement of moving objects as the experiment 
usually uses high speed camera and has a significant amount of data needing labeling. Some automated 
masking procedures are developed to help with these scenario. One of them involves fitting predetermined 
polynomial to the PIV data as the output mask. However this method requires preexisting knowledge about 
the motion and shape of the object measured, which would be impractical in some cases.

Computer vision has been proposed as a measure for mask generation in PIV experiments. The proposed algorithm 
uses the Segment Anything Model developed by Meta AI capable of zero-shot generalization, to create masks 
around bounding points determined by the Grounding-Dino model, capable of identifying location of objects 
using natural language input. This inherently simplifies the workflow of the masking procedure and provides 
alternative measure to masking objects in motion in PIV experiments. 

This paper analyzes the aforementioned computer vision algorithm used in PIV experiment by adapting 
it to a python based PIV solver. The output from the modified solver will then be validated against 
manual masking and polynomial fitting to obtain the final conclusion regarding the feasibility of using 
computer vision for PIV experiments.

\chapter{Literature Review}


\chapter{Methodology}
Describe how the work was conducted.
\section{Programming Environment Setup}
\section{Code Preparation}
\section{Validation}
\subsection{Particle Disparity}
\subsection{Correlation Statistics}

\chapter{Results}
Present results and findings.

\chapter{Discussion}
Interpretation and discussion of results.

\chapter{Conclusions}
Summary of findings and conclusions.

% ====================
% References
% ====================
\chapter*{References}
\addcontentsline{toc}{chapter}{References}

% ====================
% Appendices
% ====================
\appendix

\chapter{Appendix A}
Begin each appendix on a separate page and label each as Appendix A, Appendix B, etc.

\chapter{Appendix B}
Additional material.

\end{document}